The binary liquid model for gravity-driven microchannel simulations

### 2010-10-14 Text/paper.tex
Specified all the necessary benchmarks.

After resolving the interface one can  calculate the
  velocity from the capillary number as:
  \begin{equation}
  U_{bubble}=0.005 \frac{\gamma}{\mu_{slug}}=0.005
\frac{0.0377}{0.66666}=2.82\,10^{-4},
  \end{equation}
  where $\mu_{slug}=1/3 (2.5-0.5)=0.6666$.
  This velocity implies the following pressure gradient calculated from the
  Poisuielle flow solution:
  \begin{equation}
  \begin{aligned}
  &U_{bubble}=\frac{H^2}{8\mu} \frac{\mathrm{d}P}{\mathrm{d}x}=\frac{Ny^2}{8/3
  (\tau_{liq}-1/2)}\frac{\mathrm{d}P}{\mathrm{d}x}\\
  &\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{Ny^2}\gamma Ca
  \end{aligned}
  \end{equation}
  Therefore the pressure gradient established is the following:
  \begin{equation}
  \begin{aligned}
  \frac{\mathrm{d}P}{\mathrm{d}x}=9.42\, 10^{-9}.
  \end{aligned}
  \end{equation}
  Note that in the case of large grids  height resolution is directly
involved in	
the physical time step as:
\begin{equation}
\Delta t =\frac{U_{LBM}}{U_{phys}} \Delta x ,
\end{equation}
where for example the real velocities in the physical world can reach
approximately $1$ m/s and physical channel height upto $1$ mm. In this case one
can easily approximate the physical time step:
\begin{equation}
\Delta t = 7.05 \, 10^{-10} \,\mathrm{s}
\end{equation}
which is a small time step. The typical simulation needs approximately
$100,000$ multiplication time steps to come to the steady state solution.

@@

After choosing the reference parameters, the grid refinement needs to keep the
same the same macroscopic parameters as capillary number and viscosities ratio.
Therefore the simulations were performed with grid
numbers $Ny=102,127,152,177,202,227$, corresponding to the
effective channels widths as $H_{eff}=100,125,150,175$,
$Nx=1501,1876,2251,2625,3000,3375=15
H_{eff}$. It is easy to check
that keeping all liquid viscosities the same yields the following quantity to
be a
constant while doing the grid refinement
$H_{eff}^2\frac{\mathrm{d}P}{\mathrm{d}x}=(N_y-2)^2\frac{\mathrm{d}P}{\mathrm{d}
x } =Const$.
{\color{red} Michal, please add some results here and description to it as well.
The results for the force driven flows velocity phase profiles are shown in
Fig. \ref{fig:grid:profiles}. The corresponding ratios to the effective channel
width (without bounce-back nodes) is as $0.0809472165313,
0.0708111118485, 0.0678483852412, 0.0664499716904$. One can see
that for the channel widths as $149,198$, the results are convergent. The
velocities in the center of the bubble are $0.004176469553,
0.00401004133, 0.003969909065, 0.00394134433$, which corresponds
to the $Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}=\frac{\frac{2}{3}\,
0.0045}{0.03771}=0.069$, which is slightly higher when for the assumed
profile. However, if we define Capillary number through the velocity of the
slug, then the Capillary number will have another value. The velocities of the
slug are $0.003411444831,0.003412693869,0.003420338754,0.003425757312$ and
Capillary number defined through these velocities is $0.0602$. 
}
Let us calculate to which extent we need to refine the interface to obtain
convergent results. The interface itself occupies approximately $5 \xi$, where
$\xi=\sqrt{k/A}=1$. This interface width divided to the effective channel width
($5\xi/H_{eff}$) is as follows {\color{red} Please add new values here
$0.102,0.051,0.034,0.025$ } for the given
$H_{eff}$. Let us calculate the interface width ratio to the film thickness as
$5\xi/H_{film}$ is as follows
{\color{red} Please add here new values $1.2605,  0.7205,  0.501,  0.3839$}.
Therefore, one needs to
resolve the interface as {\color{red} Please give number here $40\%$} of the
expected film width for simulations to be converged.
{\color{red} If we need this pictures???
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_49.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_98.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_147.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_196.eps}\\
\caption{Do we need these pictures? Grid refined profiles for the effictive
channel widths
$H_{eff}=49,98,147,196$.\label{fig:grid:profiles}}
\end{figure}
}

\section{Capillary number region}

{\color{red} The next step is to perform calculations for different Capillary
numbers to restore necessary characteristics as it's seen in Fig.
\ref{fig:giavedoni:planar} and \ref{fig:heil:planar}. Also note that grid
refinement is done for the gravity driven flows, which can have pretty
different characteristics in comparison with pressure simulations (unstable
for the grid refinement - need to adjust parameters)}.

This section is devoted to the study of different Capillary number. We refer to
grid refinement section where we obtained that the interface width should be
at most $40$ percent of the interface width. For the benchmark results we
suggest the following Capillary numbers as:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8,1.0
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows (we take the half width as it's done in the grid refinement section):
$0.04,0.06,0.08,0.1,0.12,0.13,0.15$. $5$ lattice boltzmann units occupy
$40\%$ of the interface thickness. Therefore the grid size should be as
following $314\mathrm{x}4681$,$210\mathrm{x}3121$,
$158\mathrm{x}2341$, $127\mathrm{x}1876$, $106\mathrm{x}1561$,
$98\mathrm{x}1441$,$85\mathrm{x}1246$.

To utilize previous results to properly initialize simulations to run one need
to do some modifications. The result is that for the grid with $H_{eff}=196$ we
obtained the film width as $0.0685$ and velocity in the center of the bubble as
$0.0045$. The force gradient was $6\, 10^{-6} /16$. The predicted Capillary
number was $0.05$ and the actual one is $0.0795$. But we performed simulations
according the assumed value of $0.05$. Let us perform some correlations to
calculate how the system needs to be initialized. 
\begin{equation}
\begin{aligned}
&Ca_{lit} \propto U_{slug}\\
&U_{slug} \propto \frac{\mathrm{d}P}{\mathrm{d}x} Ny^2 
&Ca_{lit} \propto \frac{\mathrm{d}P}{\mathrm{d} x} Ny^2 \text{ or }\\
\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{Ca_{lit}}{Ny^2}
\end{aligned}
\end{equation}
Therefore the initialized consistent pressure gradients can be taken from
previous consistent simulations:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6\,10^{-6}/16 \frac{Ca_{literature}}{0.05}
\frac{196^2}{Ny^2}=0.28812 \frac{Ca_{literature}}{Ny^2}
\end{equation}
Note that $Ny$ is calculated through the expected resolution of the interface
in comparison with the interface thickness which itself is based on
Capillary number simulations. In terms of time the steady state succesfull
simulation for the grid $196$ was obtained after $200,000$ steps. The physical
time is as follows:
\begin{equation}
\begin{aligned}
&\Delta t=\frac{U_{slug,LB} \Delta X}{U_{phys}} \propto \frac{1}{Ny}\\
&N_{iter}=200,000 \frac{Ny}{196}\approx 1020 Ny\\
&N_{output}=51 Ny\\
\end{aligned}
\end{equation}

Steady simulations were obtained for the following Capillary numbers
$0.03,0.05,0.08,0.1$ with the film thicknesses as
$0.0337433850478, 0.063192148642, 0.0799078589211, 0.0891674460655$ which are
quite close to the predicted one $0.04,0.06,0.08,0.1$. The thing is to identify
the Capillary numbers associated with those numbers. The velocity in the
centers are $0.00209258774,0.003826643811,0.006506324324,0.008333889077$. The
Capillary numbers associated with these velocities are $0.036992074529545796, 
0.067646144698590829,0.1150166512524845,0.14732373700007995$, which again a bit
overpredictive but consistent. The bulk liquid velocities for the simulation
are $0.001947507726,0.003364703007,0.005483194352,0.00687516499$. The capillary
numbers associated with those velocities are slightly less than with the bubble
are as follows:$0.034427397986694822, 0.059480107823211698,
0.096930097721574432, 0.12153689465513355$. We can define the average capillary
number defined through the bubble capillary and slug capillaries numbers as
$Ca_{aver}=\frac{Ca_{bubble}+Ca_{slug}}{2}$. The fig.
\ref{fig:capillary:simple} represents the thickness against the Capillary
number which mimics the curve behavior for the Capillary number dependance as
indicated in Fig. \ref{fig:giavedoni:planar}.
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/capillary_thickness_simple.eps}
\hfill
\includegraphics[width=0.47\textwidth]{Figures/capillary_range.eps}
\caption{Thickness versus the capillary number for different scalings based on
the average capillary number. \label{fig:capillary:simple}}
\end{figure}

\subsection{The influence of the force}
\begin{description}
 \item 
On the grid $198\mathrm{x}2941$ and the initial film width as $20$ units
the
influence of the force is studied. $16$ different values of force are examined,
which have the following expression $\frac{0.000006}{16} i$, where $i=1 \dots
16$. The system is allowed to come to the equilibrium after $200,000$ steps. The
goal is to study the influence of the force on the velocity and therefore the
capillary number. Unfortunately in the first case only a few simulations are
stable, i.e.
$i=1,2$ is stable. The results for the interface thicknesses are
$0.0700122222668,0.0985152303286$ with the velocities associated as
$0.004490013864,0.009597299475$ and slug velocities as
$0.003861354387,0.006350100792$. Those numbers correspond to the bubble
capillary numbers as $0.079372981271400328, 0.16965788849626481$ and slug
capillary numbers as $0.068259746790303111, 0.11225498328103167$. The average
capillary numbers are $0.07381636,0.14095644$.

\item
On the grid $394\mathrm{x}5881$ and the initial film width as $20+4 i$,where
$i=1 \dots 5$ units the
influence of the force is studied. The force is scheduled as
$\frac{0.000006}{128}+i \frac{0.000006}{640}$.The intention is to cover the
calculation of the Capillary numbers in the range $0.03,0.035,0.04,0.045,0.05$. 
$5$ different values of force are examined. The system is allowed to come to the
equilibrium after $400,000-40,000 i$ steps. The associated thicknesses were as
it follows
$0.0488915027016,0.0538098132568,0.0587100833678,0.0615470184196,
0.0661331899123$. Bubble velocities are
$0.002592856205,0.003077834398,0.003562975124,0.004034533823,0.004470657603$.
Slug velocities are
$0.002337542358,0.002752687109,0.003158125555,0.003552413499,0.003926980914$.
Bubble Capillary numbers are $0.04583566,  0.05440894,  0.0629851 , 
0.07132116, 0.07903081$; slug Capillary numbers are $0.0413223 ,  0.04866109, 
0.0558283, 0.06279839, 0.06941987$. The average capillary numbers are
$0.04357898, 0.05153502, 0.0594067, 0.06705977, 0.07422534$.
\end{description}

All the range of available Capillary numbers are shown in Fig.
\ref{fig:capillary:simple}. The figure looks consistent with different
scalings and provide good results.

\subsection{The influence of the wall gradient}
The influence of the wall gradient. We examined the wall gradient influence on
the standard grid $198\mathrm{x}2941$ and the initial film width as $20$
lattice boltzmann units. We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
$0.0709130255276, 0.0708903443305, 0.0708661222722,
0.0708369188112, 0.0707962325316, 0.0707266326981, 0.0705839443249,
0.0702489349415, 0.0697553433989$. For the wall gradients $0.8$ and $1.0$ the
values are NAN. The negative values of the phase gradient are preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$. In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one.

\subsection{The flow driven by the pressure difference}
The details of imposing pressure boundaries for the binary liquid model is
given in Section \ref{appendix-pressure}.

\subsubsection{The influence of initial bubble width. Easy parameters to check}
Here we impose absolutely the same parameters as for gravity driven flow.
However instead of pressure gradient one needs to put different densities at
the inlet and the outlet which can be easily calculated from the pressure
gradient as follows:
\begin{equation}
\begin{aligned}
&\rho_{inlet}=1+3 Nx \frac{\mathrm{d}P}{\mathrm{d}x}=3\, 750\, 6\,
10^{-6}=1.0135\\
&\rho_{outlet}=1.
\end{aligned}
\end{equation}

Some pictures after $40000$ steps for the pressure driven flows for different
initialization of bubble width as $Ny-12$, $Ny-20$, $Ny-28$.
\begin{figure}
\includegraphics*[bb=18 350 594 450,
width=0.97\textwidth]{Figures/pressure_width_6.eps}
\includegraphics*[bb=18 350 594 450,
width=0.97\textwidth]{Figures/pressure_width_10.eps}
\includegraphics*[bb=18 350 594 450,
width=0.97\textwidth]{Figures/pressure_width_14.eps}
\caption{The phase plots for different bubble widths as $Ny-12$,$Ny-20$ and
$Ny-28$.}
\end{figure}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/plane_pressure_width_6.eps}
\includegraphics[width=0.47\textwidth]{Figures/plane_pressure_width_10.eps}
\begin{center}
\includegraphics[width=0.47\textwidth]{Figures/plane_pressure_width_14.eps}
\end{center}
\caption{The phase profiles for different initialization parameters as the
bubble width $Ny-12$,$Ny-20$ and $Ny-28$.
\label{fig:phase:profiles:different:widths:pressure}}
\end{figure}
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/vel_bubble_pressure_width_6.eps}
\hfill
\includegraphics[width=0.47\textwidth]{Figures/vel_bulk_pressure_width_6.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/vel_bubble_pressure_width_10.eps}
\hfill
\includegraphics[width=0.47\textwidth]{Figures/vel_bulk_pressure_width_10.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/vel_bubble_pressure_width_14.eps}
\hfill
\includegraphics[width=0.47\textwidth]{Figures/vel_bulk_pressure_width_14.eps}\\
\caption{The velocity profiles in bulk and bubble for different initialization
parameters as the
bubble width $Ny-12$,$Ny-20$ and $Ny-28$.
\label{fig:velocity:profiles:different:widths:pressure}}
\end{figure}

\section{Appendix I. Pressure boundaries conditions}
\label{appendix-pressure}
Bulk pressure for the binary liquid model is a function not only of density
but the phase field as well. Thus, one of the possible ways to fix the pressure
boundary condition is to fix density and phase at the inleat and at the outlet.
The pressure difference is introduced through the difference in densities
keeping phases at the inlet and at the outlet the same. One can introduce the
pressure difference through the phase, however it's unphysical since the phase
field is governed by passive advection-diffusion equation, where velocity is
given from the hydrodynamic simulations.

We examined many different pressure boundaries conditions, including Zou-He BC
\cite{zouhe-boundary,harting-pressure}, equilibrium conditions for
the phase field, etc. However, the stable situation was obtained only with the
boundary conditions by \citeauthor{guo-pressure} \cite{guo-pressure,
guo-boundary-conditions}. The idea of the boundary conditions is simple: the
coming populations to domain are decomposed to the equilibrium and
non-equilibrium part:
\begin{equation}
f_i=f_i^{eq}(\rho_{wall},\bm{u}_{wall})+f_i^{neq}.
\end{equation}
The incoming population after the collision is changed due to collision:
\begin{equation}
f_i=f_i^{eq}(\rho_{wall},\bm{u}_{wall})+f_i^{neq} (1-\omega).
\end{equation}
The method is called extrapolation as the wall macroscopic parameters are
extrapolated from fluid using first or second accuracy numerical stencils. If
the pressure boundary condition is specified then it specifies $\rho_{wall}$ as
well extrapolating the wall velocity $\bm{u}_{wall}$ from nearest neighbours.
The same goes for the velocity boundary conditions, where velocity
$\bm{u}_{wall}$ is specified and $\rho_{wall}$ is extrapolated from the fluid.

It is pretty straightforward to obtain non-equilibrium contribution from the
fluid, however the equilibrium for the wall side needs special treatment. If
one wants to take the hydrodynamic equilibrium, the numerical scheme blows
up. Therefore, one needs to construct the equilibrium function as it's given
for the binary liquid model. The binary liquid model equilibrium contains local
density, local phase and phase laplacians and gradients. The pressure boundary
conditions specify the local phase and the local density. Therefore, we
extrapolate not only velocity to construct the equilibrium, but phase laplacian
and gradients. This situation produces stable simulations to be validated in
the future. 
\bibliographystyle{plainnat}
\bibliography{paper}

>>>>

After resolving the interface one can  calculate the
  velocity from the capillary number as:
  \begin{equation}
  U_{bubble}=0.005 \frac{\gamma}{\mu_{slug}}=0.005
\frac{0.0377}{0.66666}=2.82\,10^{-4},
  \end{equation}
  where $\mu_{slug}=1/3 (2.5-0.5)=0.6666$.
  This velocity implies the following pressure gradient calculated from the
  Poisuielle flow solution:
  \begin{equation}
  \begin{aligned}
  &U_{bubble}=\frac{H^2}{8\mu} \frac{\mathrm{d}P}{\mathrm{d}x}=\frac{Ny^2}{8/3
  (\tau_{liq}-1/2)}\frac{\mathrm{d}P}{\mathrm{d}x}\\
  &\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{Ny^2}\gamma Ca
  \end{aligned}
  \end{equation}
  Therefore the pressure gradient established is the following:
  \begin{equation}
  \begin{aligned}
  \frac{\mathrm{d}P}{\mathrm{d}x}=9.42\, 10^{-9}.
  \end{aligned}
  \end{equation}
  Note that in the case of large grids  height resolution is directly
involved in	
the physical time step as:
\begin{equation}
\Delta t =\frac{U_{LBM}}{U_{phys}} \Delta x ,
\end{equation}
where for example the real velocities in the physical world can reach
approximately $1$ m/s and physical channel height upto $1$ mm. In this case one
can easily approximate the physical time step:
\begin{equation}
\Delta t = 7.05 \, 10^{-10} \,\mathrm{s}
\end{equation}
which is a small time step. The typical simulation needs approximately
{\color{red} $100,000$} time steps to come to the steady state solution.

@@

After choosing the reference parameters, the grid refinement needs to keep the
same the same macroscopic parameters as capillary number and viscosities ratio.
Therefore the simulations were performed with grid
numbers $N_y=102,127,152,177,202,227$, corresponding to the
effective channels widths as $H_{eff}=100,125,150,175,200,225$,
$N_x=1501,1876,2251,2626,3001,3376=15
H_{eff}+1$. It is easy to check
that keeping all liquid viscosities the same yields the following quantity to
be a
constant while doing the grid refinement
$H_{eff}^2\frac{\mathrm{d}P}{\mathrm{d}x}=(N_y-2)^2\frac{\mathrm{d}P}{\mathrm{d}
x } =Const$.
{\color{red} Michal, please add some results here and description to it as well.
The results for the force driven flows velocity phase profiles are shown in
Fig. \ref{fig:grid:profiles}. The corresponding ratios to the effective channel
width (without bounce-back nodes) is as $0.0809472165313,
0.0708111118485, 0.0678483852412, 0.0664499716904$. One can see
that for the channel widths as $149,198$, the results are convergent. The
velocities in the center of the bubble are $0.004176469553,
0.00401004133, 0.003969909065, 0.00394134433$, which corresponds
to the $Ca=\frac{\mu_{liq} U_{bubble}}{\gamma}=\frac{\frac{2}{3}\,
0.0045}{0.03771}=0.069$, which is slightly higher when for the assumed
profile. However, if we define Capillary number through the velocity of the
slug, then the Capillary number will have another value. The velocities of the
slug are $0.003411444831,0.003412693869,0.003420338754,0.003425757312$ and
Capillary number defined through these velocities is $0.0602$. 
}
Let us calculate to which extent we need to refine the interface to obtain
convergent results. The interface itself occupies approximately $5 \xi$, where
$\xi=\sqrt{k/A}=1$. This interface width divided to the effective channel width
($5\xi/H_{eff}$) is as follows {\color{red} Please add new values here
$0.102,0.051,0.034,0.025$ } for the given
$H_{eff}$. Let us calculate the interface width ratio to the film thickness as
$5\xi/H_{film}$ is as follows
{\color{red} Please add here new values $1.2605,  0.7205,  0.501,  0.3839$}.
Therefore, one needs to
resolve the interface as {\color{red} Please give number here $40\%$} of the
expected film width for simulations to be converged.
{\color{red} If we need this pictures???
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_49.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_98.eps}\\
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_147.eps}\hfill
\includegraphics[width=0.47\textwidth]{Figures/grid_phase_prof_196.eps}\\
\caption{Do we need these pictures? Grid refined profiles for the effictive
channel widths
$H_{eff}=49,98,147,196$.\label{fig:grid:profiles}}
\end{figure}
}

\subsection{The influence of the wall gradient}
Once the procedure of how to resolve the interface gradient is known, we want
to examine the influence of the phase gradient, i.e. the wettability of the
wall, to the film thickness. We examined the
wall gradient influence on
the standard grid $202\mathrm{x}3001$ and the initial film width as
{\color{red} Take the value from previous calculations $20$}
lattice boltzmann units. We examined $11$ different values for the wall
gradient ranging from $-1$ to $1$. The results are consistent among all the
wall gradients given that the interface is resolved in the right way. For the
given wall gradients the values of interface thicknesses are
{\color{red} Change these numbers $0.0709130255276, 0.0708903443305,
0.0708661222722,
0.0708369188112, 0.0707962325316, 0.0707266326981, 0.0705839443249,
0.0702489349415, 0.0697553433989$}. For the wall gradients $0.8$ and $1.0$ the
values are NAN. The negative values of the phase gradient are preferable, as
far as the phase of the liquid adjacent to the wall has the value of $1$. That
means that the phase values near the wall are above $1$. In case of positive
gradients the values near the wall are below $1$ and the gradient profile can
fuse with the values of the gas phase as $-1$, creating the wall stickyness,
unphysical one. {\color{red} Michal, if you want to add some pictures go ahead
with it}.

\section{The influence of different viscosities}
The results obtained earlier are taken for the liquiqs viscosity ratio $10$.
We performed the same simulations for the liquids viscosity ratio as $20$.
Parameters were taken as $\tau_{liquid}=4.5$ and $\tau_{bubble}=0.7$. 
{\color{red} The results showed that blah-blah-blah - I guess will be the same}.

\section{Capillary number region}
The purpose of this section is to validate the correlations of
\citet{giavedoni-numerical}, Fig. \ref{fig:giavedoni:planar}, and
\citet{heil-bretherton}, Fig. \ref{fig:heil:planar}, for the range of capillary
numbers. Because of limiting computational factors ({\color{red} What is the
least capillary number which is OK?}) we cannot go to the range of small
capillary numbers. However, all the other methods were validated across the
small capilary numbers and extended for the range of capillary numbers from
$0.005$ to $1.0$. Our goal is to compare the film thickness over the capillary
range from $0.03$ to $1.0$.

To perform numerical simulations we refer to
grid refinement section where we obtained that the interface width should be
at most {\color{red} $40$} percent of the interface width. For the benchmark
results we
suggest the following Capillary numbers as:
\begin{equation}
0.03,0.05,0.08,0.1,0.2,0.4,0.6,0.8,1.0\, .
\end{equation}
The corresponding approximate film widths from \cite{giavedoni-numerical} are as
follows:
$0.04,0.06,0.08,0.1,0.12,0.13,0.15$. $5$ lattice boltzmann units occupy
{\color{red} Could be another number $40\%$} of the interface thickness.
Therefore the grid size should be as
following {\color{red} Michal, different numbers would be here.
$314\mathrm{x}4681$,$210\mathrm{x}3121$,
$158\mathrm{x}2341$, $127\mathrm{x}1876$, $106\mathrm{x}1561$,
$98\mathrm{x}1441$,$85\mathrm{x}1246$ Michal, for the larger capillary
numbers such small grid is not
appropriate because of the instabilities.
}.

{\color{red} Probably we don't need the explanations about initialization here,
just to present results}
To utilize previous results to properly initialize simulations to run one need
to do some modifications. The result is that for the grid with $H_{eff}=200$ we
obtained the film width as {\color{red} Will be another number $0.0685$} and
velocity in the center of the bubble as
{\color{red} Will be another number $0.0045$}. The force gradient was
{\color{red} Probably the same number $6\, 10^{-6} /16$}. The predicted
Capillary
number was $0.05$ and the actual one based on the center velocity calculation is
{\color{red} Will be another number $0.0795$}. However, we performed simulations
according the assumed value of $0.05$. Let us perform some correlations to
calculate how the system needs to be initialized. 
\begin{equation}
\begin{aligned}
&Ca_{lit} \propto U_{slug}\\
&U_{slug} \propto \frac{\mathrm{d}P}{\mathrm{d}x} N_y^2\\ 
&Ca_{lit} \propto \frac{\mathrm{d}P}{\mathrm{d} x} N_y^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{Ca_{lit}}{Ny^2},
\end{aligned}
\end{equation}
where the index $lit$ stands for the presented in the literature in
\cite{giavedoni-numerical,heil-bretherton}. Therefore the initialized consistent
pressure gradients can be taken from
previous consistent simulations:
\begin{equation}
\frac{\mathrm{d}P}{\mathrm{d} x}=6\,10^{-6}/16 \frac{Ca_{literature}}{0.05}
\frac{200^2}{N_y^2}=0.3 \frac{Ca_{literature}}{N_y^2}
\end{equation}
Note that $N_y$ is calculated through the expected resolution of the interface
in comparison with the interface thickness which itself is based on
Capillary number simulations. In terms of time the steady state successful
simulation for the grid $202\mathrm{x}3001$ was obtained after $200,000$ steps.
The physical
time is as follows:
\begin{equation}
\begin{aligned}
&\Delta t=\frac{U_{slug,LB} \Delta X}{U_{phys}} \propto \frac{1}{N_y-2}\\
&N_{iter}=200,000 \frac{N_y-2}{200}\approx 1000 N_y\\
%&N_{output}=51 Ny\\
\end{aligned}
\end{equation}

{\color{red} That's why we need better grid for larger Capillary numbers. Steady
simulations were obtained for the following Capillary numbers
$0.03,0.05,0.08,0.1$  }with the film thicknesses as
{\color{red} $0.0337433850478, 0.063192148642, 0.0799078589211,
0.0891674460655$} which are
quite close to the predicted one $0.04,0.06,0.08,0.1$. The thing is to identify
the Capillary numbers associated with those numbers. The velocity in the
centers are $0.00209258774,0.003826643811,0.006506324324,0.008333889077$. The
Capillary numbers associated with these velocities are $0.036992074529545796, 
0.067646144698590829,0.1150166512524845,0.14732373700007995$, which again a bit
overpredictive but consistent. The fig.
\ref{fig:capillary:simple} represents the thickness against the Capillary
number which mimics the curve behavior for the Capillary number dependance as
indicated in Fig. \ref{fig:giavedoni:planar}.
\begin{figure}
\includegraphics[width=0.47\textwidth]{Figures/capillary_thickness_simple.eps}
\hfill
\includegraphics[width=0.47\textwidth]{Figures/capillary_range.eps}
\caption{{\color{red} This one to eliminate - just present here
comparison between our simulations in the longer range of capillary
numbers and Giavedoni}Thickness versus the capillary
number for different scalings based on
the average capillary number. \label{fig:capillary:simple}}
\end{figure}

\subsection{The influence of the force}

{\color{red} Michal if you find it useful - use this section. My suggestion is
to eliminate it.}
\begin{description}
 \item 
On the grid $198\mathrm{x}2941$ and the initial film width as $20$ units
the
influence of the force is studied. $16$ different values of force are examined,
which have the following expression $\frac{0.000006}{16} i$, where $i=1 \dots
16$. The system is allowed to come to the equilibrium after $200,000$ steps. The
goal is to study the influence of the force on the velocity and therefore the
capillary number. Unfortunately in the first case only a few simulations are
stable, i.e.
$i=1,2$ is stable. The results for the interface thicknesses are
$0.0700122222668,0.0985152303286$ with the velocities associated as
$0.004490013864,0.009597299475$. Those numbers correspond to the bubble
capillary numbers as $0.079372981271400328, 0.16965788849626481$. The average
capillary numbers are $0.07381636,0.14095644$.

\item
On the grid $394\mathrm{x}5881$ and the initial film width as $20+4 i$,where
$i=1 \dots 5$ units the
influence of the force is studied. The force is scheduled as
$\frac{0.000006}{128}+i \frac{0.000006}{640}$.The intention is to cover the
calculation of the Capillary numbers in the range $0.03,0.035,0.04,0.045,0.05$. 
$5$ different values of force are examined. The system is allowed to come to the
equilibrium after $400,000-40,000 i$ steps. The associated thicknesses were as
it follows
$0.0488915027016,0.0538098132568,0.0587100833678,0.0615470184196,
0.0661331899123$. Bubble velocities are
$0.002592856205,0.003077834398,0.003562975124,0.004034533823,0.004470657603$.
Bubble Capillary numbers are $0.04583566,  0.05440894,  0.0629851 , 
0.07132116, 0.07903081$.
\end{description}

\section{Conclusion}
The work presents the numerical tips and the benchmark for the
Bretherton/Taylor problem using the binary liquid lattice Botlzmann method. The
results show consistency with the already obtained numerical correlations using
other methods. Though results are specific for the binary liquid lattice
Botlzmann method but numerical tips and correlations can be used for any
continuous interface methods. The work is valuable for people simulating
microchannel flows.

\bibliographystyle{plainnat}
\bibliography{paper}
